USAMS Hybrid Source Summary

### 2021-01-25 hgis_summary.Rmd
Update summary.

The open split interface supplies a helium-co2 mixture to a split where a
capillary delivers ~10uL/min to the source and the rest is vented. The current
split starts showing "breakthrough" of lab air at around 150uL/min flow. A new open split with lower volume should have improved this, but testing is needed.

@@

First tests of displacing pure CO2 from a vial into the open split using helium
are promising. Helium flowing at 100uLm-1 produces current from 7mL of CO2 for
over 2 hours. Currents do decrease with time due to dilution, but by supplying
higher than optimal CO2 flow to the source initially, stable currents can be
maintained for some time. Targets have shown "pulses" of higher current. Not sure why this is, but I suspect it's either buildup of graphite or other available carbon on the target, or target switching to the "high state" as sometimes happens with solid targets.

@@

>>>>

The open split interface supplies a helium-co2 mixture to a split where a
capillary delivers gas to the source and the rest is vented. The current
split starts showing "breakthrough" of lab air at around 150uL/min flow. A new open split with lower volume should have improved this, but testing is needed.

@@

First tests of displacing pure CO2 from a vial into the open split using helium
are promising. Helium flowing at 100uLm-1 produces current from 7mL of CO2 for
over 2 hours. Currents do decrease with time due to dilution, but by supplying
higher than optimal CO2 flow to the source initially, stable currents can be
maintained for some time.  Setting flow to the source to 10uL/min provides excess CO2 to source until the helium dilution ratio increases to > 1:1. Another approach may be to backfill vials with helium and run at a higher dilution ratio and flow to the source. This should produce a smaller change in He:CO2 over the course of a run. MICADAS runs at 95% He:CO2, which would mean producing < 0.5mL CO2 in a 7mL vial and backfilling with helium before displacing to the source. Some intermediate dilution may be appropriate.

Targets have shown "pulses" of higher current. Not sure why this is, but I suspect it's either buildup of graphite or other available carbon on the target, or target switching to the "high state" as sometimes happens with solid targets.

@@

## To do

* Repeated measurements under identical conditions to determine reproducibility
* Test breakthrough with new open split
* Establish best helium flow for displacement
* Fine tune capillary length for best flow to source over pCO2 range of full size sample
* How to handle < 1 Atm in vials. Backfill?
* Measure test samples prepped on Gilson (7mL CO2, Atm pressure)
* Define blank, determine whether current-balance correction is needed.
* Refine normalization and error propagation for data reduction.
